The Shades of Racism in the Beauty Industry

### 2023-04-19 outputs/paper/paper.qmd
Simulated data and tests

### Simplifying Dates: Fashion Tones Dataset:
cleaned_fashion_tones<-
  cleaned_fashion_tones |>
  separate(
    col = date,
    into = c("Month", "Day", "Year"),
    sep = "/"
  ) |>
  mutate(cleaned_fashion_tones, clean_date = paste(Year, Month, Day, sep = "-"))
  str(cleaned_fashion_tones$clean_date)

>>>>

### Simplifying Dates: Fashion Tones Data Set:
cleaned_fashion_tones<-
  cleaned_fashion_tones |>
  separate(
    col = date,
    into = c("Month", "Day", "Year"),
    sep = "/"
  ) |>
  mutate(cleaned_fashion_tones, clean_date = paste(Year, Month, Day, sep = "-"))
  str(cleaned_fashion_tones$clean_date)
